### 2016-09-15 revision/mirror-descent.tex
new directory for revision and first draft

\begin{algorithm}[t]
\caption{\textsc{Mirror Descent with Varying Regularizer}}
\label{algorithm:mirror-descent-varying-regularizer}
\begin{algorithmic}[1]
\REQUIRE Non-empty closed convex set $K \subseteq V$
\STATE Choose a regularizer $R_0:K \to \R$
\STATE $w_1 \leftarrow \argmin_{w \in K} R_0(w)$
\FOR{$t=1,2,3,\dots$}
\STATE Predict $w_t$
\STATE Observe $\ell_t \in V^*$
\STATE Choose a regularizer $R_t:K \to \R$
\STATE $w_{t+1} \leftarrow \argmin_{w \in K} \left( \langle \ell, w \rangle + \Breg_{R_t}(w, w_t) \right)$
\ENDFOR
\end{algorithmic}
\end{algorithm}

\textsc{Mirror Descent} (MD) is a generic algorithm similar to \textsc{FTRL}
but quite different in details. The algorithm is stated as
Algorithm~\ref{algorithm:mirror-descent-varying-regularizer}. The algorithm is
parametrized by a sequence $\{R_t\}_{t=0}^\infty$ of convex functions $R_t:K
\to \R$ called \emph{regularizers}. Each regularizer $R_t$ can depend on past
loss vectors $\ell_1, \ell_2, \dots, \ell_t$ in an arbitrary way. If $R_t$ is
not differentiable\footnote{Note that this can happen even when $R_t$ is a
restriction of a differentiable function defined on a superset of $K$.  If $K$
is bounded and closed, $R_t$ fails to be differentiable at the boundary of $K$.
If $K$ is a subset of an affine subspace of a dimension smaller than the
dimension of $V$, then $R_t$ fails to be differentiable everywhere.}, the
Bregman divergence, $\Breg_{R_t}(u,v) = R_t(u) - R_t(v) - \langle \grad R_t(v),
u - v \rangle$ needs to be defined. This is done by choosing a subgradient map
$\grad R_t:K \to V$, i.e., a function such that $\grad R_t(w)$ is a subgradient
of $R_t$ at a point $w$. If $R_t$ is a restriction of a differentiable function
$R'_t$, it is convenient to define $\grad R_t(w) = \grad R'_t(w)$ for all $w
\in K$. The following lemma bounds regret of \textsc{MD}.  Proof can be found
in~\cite{Rakhlin-Sridharan-2009,Duchi-Shalev-Shwartz-Singer-Tewari-2010}.  For
completeness we give a proof in~\ref{section:mirror-descent-proofs}.

\begin{lemma}[Regret of \textsc{MD}]
\label{lemma:mirror-descent-regret}
Algorithm~\ref{algorithm:mirror-descent-varying-regularizer} satisfies, for any
$u \in K$,
$$
\Regret_T(u)
\le
\sum_{t=1}^T \langle \ell_t, w_t - w_{t+1} \rangle - \Breg_{R_t}(w_{t+1}, w_t) + \Breg_{R_t}(u,w_t) - \Breg_{R_t}(u, w_{t+1}) \; .
$$
\end{lemma}

Several existing algorithms are special cases of \textsc{MD}.  For example,
\textsc{Hedge} is an instance of \textsc{MD} for the probability simplex $K =
\{ w \in \R^d ~:~ w_j \ge 0, \sum_{j=1}^d w_j = 1 \}$ with negative entropy
regularizer $R_t(w) = \frac{1}{\eta} \sum_{j=1}^d w_j \ln w_j$ where $\eta > 0$
is a (constant) learning rate. Note that this algorithm is \emph{not}
scale-free.

The most prominent instance of \textsc{MD} is \textsc{Projected Gradient
Descent} defined by the recurrence
$$
w_{t+1} = \Pi_K \left( w_t - \eta_t \ell_t \right) \; ,
$$
where $\Pi_K(x) = \argmin_{y \in K} \|x-y\|_2$ is the Euclidean projection to
$K$ and $\eta_t > 0$ is the step size.  \textsc{Projected Gradient Descent} is
an instance of \textsc{MD} with regularizer $R_t(w) =
\frac{1}{2\eta_t}\|w\|_2^2$.  A special case of \textsc{Projected Gradient
Descent} with step size $\eta_t = \frac{1}{\sqrt{t}}$ is \textsc{Generalized
Infinitesimal Gradient Ascent} (GIGA)~\cite{Zinkevich-2003}.  Full-matrix and
diagonal versions of \textsc{AdaGrad with Composite MD
Update}~\cite{Duchi-Hazan-Singer-2011} are an instances of \textsc{MD} for any
bounded $K$ with regularizers
$$
R_t(w) = \frac{1}{2} w^\top \left(\sum_{i=1}^t \ell_i \ell_i^\top \right)^{1/2} \!\!\!\! w
\qquad \text{and} \qquad
R_t(w) = \frac{1}{2} \sum_{j=1}^d w_j^2 \sqrt{ \sum_{i=1}^t \ell_{i,j}^2}
$$
respectively. The diagonal version is simply the per-coordinate construction
applied to the one-dimensional version. When $d=1$, both algorithms are
equivalent to
\begin{equation}
\label{equation:ada-grad-regularizer}
R_t(w) = \frac{\|w\|_2^2}{2} \sqrt{\sum_{i=1}^t \|\ell_i\|_2^2 } \; .
\end{equation}
All three sequences of regularizers give a scale-free algorithm. Regularizer
\eqref{equation:ada-grad-regularizer} can be viewed as a scale-free
generalization of GIGA. That is, when $\|\ell_i\|_2
= 1$ for all $i$, \textsc{MD} with regularizer
\eqref{equation:ada-grad-regularizer} coincides with GIGA.

@@

The regret bound for \textsc{Scale-Free MD} in the
Corollary~\ref{corollary:regret-scale-free-mirror-descent} depends on
$\sup_{u,v \in K} \Breg_f(u,v)$. In contrast, the regret bounds for
\textsc{AdaFTRL} and \textsc{SOLO FTRL} in
Corollaries~\ref{corollary:ada-ftrl-regret-bound}~and~\ref{corollary:regret-solo-ftrl-bounded-set}
depend on $\sup_{u \in K} f(u)$.  Similarly, the regret bound in
Theorem~\ref{theorem:regret-scale-free-mirror-descent} for \textsc{Scale-Free
MD} depends on $\sup_{v \in K} \Breg_R(u,v)$ and the regret bounds in
Theorems~\ref{theorem:ada-ftrl-regret-bound}~and~\ref{theorem:regret-solo-ftrl}
for \textsc{AdaFTRL} and \textsc{SOLO FTRL} depend on $R(u)$. It is not hard to
show that
\begin{equation}
\label{equation:regularizer-vs-divergence}
\forall u \in K \qquad R(u) \le \sup_{v \in K} \Breg_R(u,v) \; ,
\end{equation}
provided that at the minimizer $v^* = \argmin_{v \in K} R(v)$ both $R(v^*)$ and
$\grad R(v^*)$ are zero. Indeed, in that case, $R(u) = \Breg_R(u,v^*) \le
\sup_{v \in K} \Breg_R(u,v)$.

@@

Thus, inequality \eqref{equation:regularizer-vs-divergence} implies
that---ignoring constant factors---the regret bound for \textsc{Scale-Free MD}
is inferior to the regret bounds for \textsc{AdaFTRL} and \textsc{SOLO FTRL}.
In fact, it is not hard to come up with examples where $R(u)$ is finite whereas
$\sup_{v \in K} \Breg_R(u,v)$ is infinite. We mention two such examples. The
first example is $R(w) = \frac{1}{2}\|w\|_2^2$ defined on the whole space $V$,
where for any $u \in V$, $R(u)$ is a finite value but $\sup_{v \in K}
\Breg_R(u,v) = \sup_{v \in V} \frac{1}{2}\|u-v\|_2^2 = +\infty$. The second
example is the shifted negative entropy regularizer $R(w) = \ln(d) +
\sum_{j=1}^d w_j \ln w_j$ defined on the $d$-dimensional probability simplex $K
= \{ w \in \R^d ~:~ w_j \ge 0, \sum_{j=1}^d w_j = 1 \}$, where for any $u \in
K$, $R(u)$ is finite and in fact lies in the interval $[0, \ln d]$ but
$\sup_{v \in K} \Breg_R(u,v) = \sup_{v \in K} \sum_{j=1}^d u_j \ln(u_j/v_j) = +
\infty$. We revisit these examples in the following subsection.

>>>>

Full-matrix and diagonal versions of \textsc{AdaGrad with Composite MD
Update}~\cite{Duchi-Hazan-Singer-2011} are an instances of \textsc{MD} for any
bounded $K$ with regularizers
$$
R_t(w) = \frac{1}{2} w^\top \left(\sum_{i=1}^t \ell_i \ell_i^\top \right)^{1/2} \!\!\!\! w
\qquad \text{and} \qquad
R_t(w) = \frac{1}{2} \sum_{j=1}^d w_j^2 \sqrt{ \sum_{i=1}^t \ell_{i,j}^2}
$$
respectively. The diagonal version is simply the per-coordinate construction
applied to the one-dimensional version. When $d=1$, both algorithms are
equivalent to
\begin{equation}
\label{equation:ada-grad-regularizer}
R_t(w) = \frac{\|w\|_2^2}{2} \sqrt{\sum_{i=1}^t \|\ell_i\|_2^2 } \; .
\end{equation}
All three sequences of regularizers give a scale-free algorithm. Regularizer
\eqref{equation:ada-grad-regularizer} can be viewed as a scale-free
generalization of GIGA. That is, when $\|\ell_i\|_2
= 1$ for all $i$, \textsc{MD} with regularizer
\eqref{equation:ada-grad-regularizer} coincides with GIGA.

@@

The regret bound for \textsc{Scale-Free MD} in the
Corollary~\ref{corollary:regret-scale-free-mirror-descent} depends on
$\sup_{u,v \in K} \Breg_f(u,v)$. In contrast, the regret bound for
\textsc{SOLO FTRL} in Corollary~\ref{corollary:regret-solo-ftrl-bounded-set}
depend on $\sup_{u \in K} f(u)$.  Similarly, the regret bound in
Theorem~\ref{theorem:regret-scale-free-mirror-descent} for \textsc{Scale-Free
MD} depends on $\sup_{v \in K} \Breg_R(u,v)$ and the regret bounds in
Theorem~\ref{theorem:regret-solo-ftrl}
for \textsc{SOLO FTRL} depend on $R(u)$. It is not hard to
show that
\begin{equation}
\label{equation:regularizer-vs-divergence}
\forall u \in K \qquad R(u) \le \sup_{v \in K} \Breg_R(u,v) \; ,
\end{equation}
provided that at the minimizer $v^* = \argmin_{v \in K} R(v)$ both $R(v^*)$ and
$\grad R(v^*)$ are zero. Indeed, in that case, $R(u) = \Breg_R(u,v^*) \le
\sup_{v \in K} \Breg_R(u,v)$.

@@

Thus, inequality \eqref{equation:regularizer-vs-divergence} implies
that---ignoring constant factors---the regret bound for \textsc{Scale-Free MD}
is inferior to the regret bound for \textsc{SOLO FTRL}.
In fact, it is not hard to come up with examples where $R(u)$ is finite whereas
$\sup_{v \in K} \Breg_R(u,v)$ is infinite. We mention two such examples. The
first example is $R(w) = \frac{1}{2}\|w\|_2^2$ defined on the whole space $V$,
where for any $u \in V$, $R(u)$ is a finite value but $\sup_{v \in K}
\Breg_R(u,v) = \sup_{v \in V} \frac{1}{2}\|u-v\|_2^2 = +\infty$. The second
example is the shifted negative entropy regularizer $R(w) = \ln(d) +
\sum_{j=1}^d w_j \ln w_j$ defined on the $d$-dimensional probability simplex $K
= \{ w \in \R^d ~:~ w_j \ge 0, \sum_{j=1}^d w_j = 1 \}$, where for any $u \in
K$, $R(u)$ is finite and in fact lies in the interval $[0, \ln d]$ but
$\sup_{v \in K} \Breg_R(u,v) = \sup_{v \in K} \sum_{j=1}^d u_j \ln(u_j/v_j) = +
\infty$. We revisit these examples in the following subsection.

### 2016-09-15 revision/preliminaries.tex
new directory for revision and first draft

Monotonicity of Fenchel conjugates follows easily from the definition: If
$f,g:K \to \R$ satisfies $f(w) \le g(w)$ for all $w \in K$ then $f^*(\ell) \ge
g^*(\ell)$ for every $\ell \in V^*$.

@@

>>>>

Monotonicity of Fenchel conjugates follows easily from the definition: If
$f,g:K \to \R$ satisfy $f(w) \le g(w)$ for all $w \in K$ then $f^*(\ell) \ge
g^*(\ell)$ for every $\ell \in V^*$.

@@

\subsection{Generic Mirror Descent with Varying Regularizer}

\begin{algorithm}[t]
\caption{\textsc{Mirror Descent with Varying Regularizer}}
\label{algorithm:mirror-descent-varying-regularizer}
\begin{algorithmic}[1]
\REQUIRE Non-empty closed convex set $K \subseteq V$
\STATE Choose a regularizer $R_0:K \to \R$
\STATE $w_1 \leftarrow \argmin_{w \in K} R_0(w)$
\FOR{$t=1,2,3,\dots$}
\STATE Predict $w_t$
\STATE Observe $\ell_t \in V^*$
\STATE Choose a regularizer $R_t:K \to \R$
\STATE $w_{t+1} \leftarrow \argmin_{w \in K} \left( \langle \ell, w \rangle + \Breg_{R_t}(w, w_t) \right)$
\ENDFOR
\end{algorithmic}
\end{algorithm}

\textsc{Mirror Descent} (MD) is a generic algorithm similar to \textsc{FTRL}
but quite different in details. The algorithm is stated as
Algorithm~\ref{algorithm:mirror-descent-varying-regularizer}. The algorithm is
parametrized by a sequence $\{R_t\}_{t=0}^\infty$ of convex functions $R_t:K
\to \R$ called \emph{regularizers}. Each regularizer $R_t$ can depend on past
loss vectors $\ell_1, \ell_2, \dots, \ell_t$ in an arbitrary way. If $R_t$ is
not differentiable\footnote{Note that this can happen even when $R_t$ is a
restriction of a differentiable function defined on a superset of $K$.  If $K$
is bounded and closed, $R_t$ fails to be differentiable at the boundary of $K$.
If $K$ is a subset of an affine subspace of a dimension smaller than the
dimension of $V$, then $R_t$ fails to be differentiable everywhere.}, the
Bregman divergence, $\Breg_{R_t}(u,v) = R_t(u) - R_t(v) - \langle \grad R_t(v),
u - v \rangle$ needs to be defined. This is done by choosing a subgradient map
$\grad R_t:K \to V$, i.e., a function such that $\grad R_t(w)$ is a subgradient
of $R_t$ at a point $w$. If $R_t$ is a restriction of a differentiable function
$R'_t$, it is convenient to define $\grad R_t(w) = \grad R'_t(w)$ for all $w
\in K$. The following lemma bounds regret of \textsc{MD}.  Proof can be found
in~\cite{Rakhlin-Sridharan-2009,Duchi-Shalev-Shwartz-Singer-Tewari-2010}.  For
completeness we give a proof in~\ref{section:mirror-descent-proofs}.

\begin{lemma}[Regret of \textsc{MD}]
\label{lemma:mirror-descent-regret}
Algorithm~\ref{algorithm:mirror-descent-varying-regularizer} satisfies, for any
$u \in K$,
$$
\Regret_T(u)
\le
\sum_{t=1}^T \langle \ell_t, w_t - w_{t+1} \rangle - \Breg_{R_t}(w_{t+1}, w_t) + \Breg_{R_t}(u,w_t) - \Breg_{R_t}(u, w_{t+1}) \; .
$$
\end{lemma}

Several existing algorithms are special cases of \textsc{MD}.  For example,
\textsc{Hedge} is an instance of \textsc{MD} for the probability simplex $K =
\{ w \in \R^d ~:~ w_j \ge 0, \sum_{j=1}^d w_j = 1 \}$ with negative entropy
regularizer $R_t(w) = \frac{1}{\eta} \sum_{j=1}^d w_j \ln w_j$ where $\eta > 0$
is a (constant) learning rate. Note that this algorithm is \emph{not}
scale-free.

The most prominent instance of \textsc{MD} is \textsc{Projected Gradient
Descent} defined by the recurrence
$$
w_{t+1} = \Pi_K \left( w_t - \eta_t \ell_t \right) \; ,
$$
where $\Pi_K(x) = \argmin_{y \in K} \|x-y\|_2$ is the Euclidean projection to
$K$ and $\eta_t > 0$ is the step size.  \textsc{Projected Gradient Descent} is
an instance of \textsc{MD} with regularizer $R_t(w) =
\frac{1}{2\eta_t}\|w\|_2^2$.  A special case of \textsc{Projected Gradient
Descent} with step size $\eta_t = \frac{1}{\sqrt{t}}$ is \textsc{Generalized
Infinitesimal Gradient Ascent} (GIGA)~\cite{Zinkevich-2003}.

### 2016-09-15 revision/solo-ftrl.tex
new directory for revision and first draft

When $K$ is bounded, we can choose the optimal multiple of the regularizer.  We
choose $R(w) = \lambda f(w)$ where $f$ is a $1$-strongly convex function and
optimize $\lambda$.  The result of the optimization is
Corollary~\ref{corollary:regret-solo-ftrl-bounded-set}; the proof is
in~\ref{section:solo-ftrl-proofs}.  It is similar to
Corollary~\ref{corollary:ada-ftrl-regret-bound} for \textsc{AdaFTRL}. The
scaling however is different in the two corollaries.  In
Corollary~\ref{corollary:ada-ftrl-regret-bound}, $\lambda \sim 1/(\sup_{v \in
K} f(v))$ while in Corollary~\ref{corollary:regret-solo-ftrl-bounded-set} we
have $\lambda \sim 1/\sqrt{\sup_{v \in K} f(v)}$.

@@

\begin{proof}[Proof of Theorem~\ref{theorem:regret-solo-ftrl}]
Let $\eta_t = \frac{1}{\sqrt{\sum_{i=1}^{t-1} \|\ell_i\|_*^2}}$, hence $R_t(w)
= \frac{1}{\eta_t} R(w)$.  We assume without loss of generality that
$\|\ell_t\|_* > 0$ for all $t$, since otherwise we can remove all rounds $t$
where $\ell_t = 0$ without affecting regret and the predictions of the
algorithm on the remaining rounds.  By Lemma~\ref{lemma:generic-regret-bound},
\begin{align*}
\Regret_T(u)
& \le \frac{1}{\eta_{T+1}} R(u) + \sum_{t=1}^T \left( \Breg_{R_t^*}(-L_t, -L_{t-1}) - R_t^*(-L_t) + R_{t+1}^*(-L_t) \right) \; .
\end{align*}
We upper bound the terms of the sum in two different ways.
First, by Proposition~\ref{proposition:conjugate-properties}, we have
$$
\Breg_{R_t^*}(-L_t, -L_{t-1}) - R_t^*(-L_t) + R_{t+1}^*(-L_t)
\le \Breg_{R_t^*}(-L_t, -L_{t-1})
\le \frac{\eta_t \|\ell_t\|_*^2}{2\lambda} \; .
$$
Second, we have
\begin{align*}
& \Breg_{R_t^*}(-L_t, -L_{t-1}) - R_t^*(-L_t) + R_{t+1}^*(-L_t) \\
& = \Breg_{R_{t+1}^*}(-L_t, -L_{t-1}) + R^*_{t+1}(-L_{t-1}) - R_t^*(-L_{t-1}) \\
& \qquad + \langle \nabla R_t^*(-L_{t-1})-\nabla R_{t+1}^*(-L_{t-1}), \ell_t \rangle  \\
& \le \frac{\eta_{t+1} \|\ell_t\|_*^2}{2\lambda} + \| \nabla R_t^*(-L_{t-1})-\nabla R_{t+1}^*(-L_{t-1})\| \cdot \|\ell_t\|_* \\
& = \frac{\eta_{t+1} \|\ell_t\|_*^2}{2\lambda} + \| \nabla R^*(- \eta_{t} L_{t-1})-\nabla R^*(- \eta_{t+1} L_{t-1})\| \cdot \|\ell_t\|_* \\
& \le \frac{\eta_{t+1} \|\ell_t\|_*^2}{2\lambda} + \min\left\{\frac{1}{\lambda} \|L_{t-1}\|_* \left(\eta_{t} - \eta_{t+1} \right), D\right\} \|\ell_t\|_* \; ,
\end{align*}
where in the first inequality we have used the fact that $R^*_{t+1}(-L_{t-1})
\le R_t^*(-L_{t-1})$, H\"older's inequality, and
Proposition~\ref{proposition:conjugate-properties}.  In the second inequality
we have used properties 5 and 7 of
Proposition~\ref{proposition:conjugate-properties}. Using the definition of
$\eta_{t+1}$ we have
\begin{align*}
\frac{\|L_{t-1}\|_* (\eta_{t} -\eta_{t+1})}{\lambda}
\le \frac{ \|L_{t-1}\|_*}{\lambda \sqrt{\sum_{i=1}^{t-1} \|\ell_i\|_*^2}}
\le \frac{ \sum_{i=1}^{t-1} \|\ell_i\|_*}{\lambda \sqrt{\sum_{i=1}^{t-1} \|\ell_i\|_*^2}}
\le \frac{\sqrt{t-1}}{\lambda}
\le \frac{\sqrt{T-1}}{\lambda}.
\end{align*}
Denoting by $H=\min\left\{\frac{\sqrt{T-1}}{\lambda},D\right\}$ we have
\begin{align*}
& \Regret_T(u)
\le \frac{1}{\eta_{T+1}} R(u) + \sum_{t=1}^T \min\left\{ \frac{\eta_t \|\ell_t\|_*^2}{2\lambda}, \ H \|\ell_t\|_* + \frac{\eta_{t+1} \|\ell_t\|_*^2}{2\lambda}  \right\} \\
& \le \frac{1}{\eta_{T+1}} R(u) + \frac{1}{2\lambda} \sum_{t=1}^T  \eta_{t+1} \|\ell_t\|_*^2 + \frac{1}{2\lambda} \sum_{t=1}^T \min\left\{ \eta_t \|\ell_t\|_*^2, \ 2 \lambda H \|\ell_t\|_* \right\} \\
& = \frac{1}{\eta_{T+1}} R(u) + \frac{1}{2\lambda} \sum_{t=1}^T  \frac{\|\ell_t\|_*^2}{\sqrt{\sum_{i=1}^t \|\ell_i\|_*^2}} + \frac{1}{2 \lambda} \sum_{t=1}^T \min\left\{ \frac{\|\ell_t\|_*^2}{\sqrt{\sum_{i=1}^{t-1} \|\ell_i\|_*^2}}, \ 2 \lambda H \|\ell_t\|_* \right\} \; .
\end{align*}
We bound each of the three terms separately. By definition of $\eta_{T+1}$, the
first term is $\frac{1}{\eta_{T+1}} R(u) = R(u) \sqrt{\sum_{t=1}^T
\|\ell_t\|_*^2}$.  We upper bound the second term using
Lemma~\ref{lemma:sum-of-square-roots-inverses} as
$$
\frac{1}{2\lambda} \sum_{t=1}^T  \frac{\|\ell_t\|_*^2}{\sqrt{\sum_{i=1}^t \|\ell_i\|_*^2}}
\le \frac{1}{\lambda} \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} \; .
$$
Finally, by Lemma~\ref{lemma:useful} we upper bound the third term as
$$
\frac{1}{2 \lambda} \sum_{t=1}^T \min\left\{ \frac{\|\ell_t\|_*^2}{\sqrt{\sum_{i=1}^{t-1} \|\ell_i\|_*^2}}, \ 2 \lambda \|\ell_t\|_* H \right\}
\le 3.5 H \max_{t \le T} \|\ell_t\|_* + \frac{1.75}{\lambda} \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} \; .
$$
Putting everything together gives the stated bound.
\end{proof}

>>>>

When $K$ is bounded, we can choose the optimal multiple of the regularizer.  We
choose $R(w) = \lambda f(w)$ where $f$ is a $1$-strongly convex function and
optimize $\lambda$.  The result of the optimization is
Corollary~\ref{corollary:regret-solo-ftrl-bounded-set}; the proof is
in~\ref{section:solo-ftrl-proofs}.
%It is similar to Corollary~\ref{corollary:ada-ftrl-regret-bound} for \textsc{AdaFTRL}. The scaling however is different in the two corollaries.  In Corollary~\ref{corollary:ada-ftrl-regret-bound}, $\lambda \sim 1/(\sup_{v \in K} f(v))$ while in Corollary~\ref{corollary:regret-solo-ftrl-bounded-set} we have $\lambda \sim 1/\sqrt{\sup_{v \in K} f(v)}$.

@@

\begin{proof}[Proof of Theorem~\ref{theorem:regret-solo-ftrl}]
Let $\eta_t = \frac{1}{\sqrt{\sum_{i=1}^{t-1} \|\ell_i\|_*^2}}$, hence $R_t(w)
= \frac{1}{\eta_t} R(w)$.  We assume without loss of generality that
$\|\ell_t\|_* > 0$ for all $t$, since otherwise we can remove all rounds $t$
where $\ell_t = 0$ without affecting regret and the predictions of the
algorithm on the remaining rounds.  By Lemma~\ref{lemma:generic-regret-bound},
\begin{align*}
\Regret_T(u)
& \le \frac{1}{\eta_{T+1}} R(u) + \sum_{t=1}^T \left( \Breg_{R_t^*}(-L_t, -L_{t-1}) - R_t^*(-L_t) + R_{t+1}^*(-L_t) \right) \; .
\end{align*}
We upper bound the terms of the sum in two different ways.
First, by Proposition~\ref{proposition:conjugate-properties}, we have
$$
\Breg_{R_t^*}(-L_t, -L_{t-1}) - R_t^*(-L_t) + R_{t+1}^*(-L_t)
\le \Breg_{R_t^*}(-L_t, -L_{t-1})
\le \frac{\eta_t \|\ell_t\|_*^2}{2\lambda} \; .
$$
Second, we have
\begin{align*}
\Breg_{R_t^*}&(-L_t, -L_{t-1}) - R_t^*(-L_t) + R_{t+1}^*(-L_t) \\
& = \Breg_{R_{t+1}^*}(-L_t, -L_{t-1}) + R^*_{t+1}(-L_{t-1}) - R_t^*(-L_{t-1}) \\
& \qquad + \langle \nabla R_t^*(-L_{t-1})-\nabla R_{t+1}^*(-L_{t-1}), \ell_t \rangle  \\
& \le \frac{\eta_{t+1} \|\ell_t\|_*^2}{2\lambda} + \| \nabla R_t^*(-L_{t-1})-\nabla R_{t+1}^*(-L_{t-1})\| \cdot \|\ell_t\|_* \\
& = \frac{\eta_{t+1} \|\ell_t\|_*^2}{2\lambda} + \| \nabla R^*(- \eta_{t} L_{t-1})-\nabla R^*(- \eta_{t+1} L_{t-1})\| \cdot \|\ell_t\|_* \\
& \le \frac{\eta_{t+1} \|\ell_t\|_*^2}{2\lambda} + \min\left\{\frac{1}{\lambda} \|L_{t-1}\|_* \left(\eta_{t} - \eta_{t+1} \right), D\right\} \|\ell_t\|_* \; ,
\end{align*}
where in the first inequality we have used the fact that $R^*_{t+1}(-L_{t-1})
\le R_t^*(-L_{t-1})$, H\"older's inequality, and
Proposition~\ref{proposition:conjugate-properties}.  In the second inequality
we have used properties 5 and 7 of
Proposition~\ref{proposition:conjugate-properties}. Using the definition of
$\eta_{t+1}$ we have
\begin{align*}
\frac{\|L_{t-1}\|_* (\eta_{t} -\eta_{t+1})}{\lambda}
\le \frac{ \|L_{t-1}\|_*}{\lambda \sqrt{\sum_{i=1}^{t-1} \|\ell_i\|_*^2}}
\le \frac{ \sum_{i=1}^{t-1} \|\ell_i\|_*}{\lambda \sqrt{\sum_{i=1}^{t-1} \|\ell_i\|_*^2}}
\le \frac{\sqrt{t-1}}{\lambda}
\le \frac{\sqrt{T-1}}{\lambda}.
\end{align*}
Denoting by $H=\min\left\{\frac{\sqrt{T-1}}{\lambda},D\right\}$ we have
\begin{align*}
& \Regret_T(u)
\le \frac{1}{\eta_{T+1}} R(u) + \sum_{t=1}^T \min\left\{ \frac{\eta_t \|\ell_t\|_*^2}{2\lambda}, \ H \|\ell_t\|_* + \frac{\eta_{t+1} \|\ell_t\|_*^2}{2\lambda}  \right\} \\
& \le \frac{1}{\eta_{T+1}} R(u) + \frac{1}{2\lambda} \sum_{t=1}^T  \eta_{t+1} \|\ell_t\|_*^2 + \frac{1}{2\lambda} \sum_{t=1}^T \min\left\{ \eta_t \|\ell_t\|_*^2, \ 2 \lambda H \|\ell_t\|_* \right\} \\
& = \frac{1}{\eta_{T+1}} R(u) + \frac{1}{2\lambda} \sum_{t=1}^T  \frac{\|\ell_t\|_*^2}{\sqrt{\sum_{i=1}^t \|\ell_i\|_*^2}} + \frac{1}{2 \lambda} \sum_{t=1}^T \min\left\{ \frac{\|\ell_t\|_*^2}{\sqrt{\sum_{i=1}^{t-1} \|\ell_i\|_*^2}}, \ 2 \lambda H \|\ell_t\|_* \right\} \; .
\end{align*}
We bound each of the three terms separately. By definition of $\eta_{T+1}$, the
first term is $\frac{1}{\eta_{T+1}} R(u) = R(u) \sqrt{\sum_{t=1}^T
\|\ell_t\|_*^2}$.  We upper bound the second term using
Lemma~\ref{lemma:sum-of-square-roots-inverses} as
$$
\frac{1}{2\lambda} \sum_{t=1}^T  \frac{\|\ell_t\|_*^2}{\sqrt{\sum_{i=1}^t \|\ell_i\|_*^2}}
\le \frac{1}{\lambda} \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} \; .
$$
Finally, by Lemma~\ref{lemma:useful} we upper bound the third term as
$$
\frac{1}{2 \lambda} \sum_{t=1}^T \min\left\{ \frac{\|\ell_t\|_*^2}{\sqrt{\sum_{i=1}^{t-1} \|\ell_i\|_*^2}}, \ 2 \lambda \|\ell_t\|_* H \right\}
\le 3.5 H \max_{t \le T} \|\ell_t\|_* + \frac{1.75}{\lambda} \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} \; .
$$
Putting everything together gives the stated bound.
\end{proof}
